\documentclass[openany]{book}

\input{../../src/main.tex}
\loadLuacode{../../src/}

\begin{document}

The newEntity command gives an entity a name, which is a good start, but not enough to fill it with life. Introducing:
\begin{verbatim}
	\addDescriptor{descriptor}{description}
\end{verbatim}
Using this command after a newEntity command adds a description to the entity. Both descriptor and description can contain almost arbitrary \TeX{} code.\footnote{Because the compiler evaluates them only once the description is printed during the generation of the automated chapters. This has a downside: If the code inside a description contains an error, the compiler will always put it in the line where automatedChapters is called. Debugging can become a bit tricky.}

For example, let us add some descriptors to \reference{sting} and \mention{glamdring}.

\begin{verbatim}
\newEntity{items}{sting}{}{Sting}

\addDescriptor{Appearance}{A short sword that glows when \nameref{orc}s are nearby.}

\addDescriptor{Engraving}{Woe to those who dislike apples!}

\newEntity{items}{glamdring}{}{Glamdring}

\addDescriptor{Etymology}{Sindarin for noise-hammer.}

\newEntity{species}{orc}{}{Orc}
\end{verbatim}

\newEntity{items}{sting}{}{Sting}

\addDescriptor{Appearance}{A short sword that glows when \nameref{orc}s are nearby.}

\addDescriptor{Engraving}{Woe to those who dislike apples!}

\newEntity{items}{glamdring}{}{Glamdring}

\addDescriptor{Etymology}{Sindarin for noise-hammer.}

\newEntity{species}{orc}{}{Orc}

\LoreTex{} prints only the descriptors of entities referred to by the reference command, sorted alphabetically. You may notice, though, that the description of \reference{sting} mentions another entity, which is therefore also put into the Only Mentioned chapter at the end.

The \TeX{} command generated when printing entity entries is subsubsection, and the descriptors are printed as paragraph. In the unmodified book class they look the same, so I personally prefer to use the memoir class instead, and add the following preamble:
\begin{verbatim}
\setsecnumdepth{subsubsection} %the deepest level still numbered
\setafterparaskip{0.01cm} %force linebreak after paragraph
%defines the style of the headers:
\setsecheadstyle{\LARGE\bfseries\scshape}
\setsubsecheadstyle{\Large\bfseries\scshape}
\setsubsubsecheadstyle{\Large\bfseries\scshape}
\setparaheadstyle{\large\bfseries\scshape}
\setsubparaheadstyle{\bfseries}
\end{verbatim}
The details are, of course, entirely up to the user.

\automatedChapters{}

\end{document}